Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-07-05 ijar-npb-ms.tex
final tweaks

Thus, Figures \ref{fig:need-to-opt-1}, \ref{fig:need-to-opt-2} and \ref{fig:need-to-opt-3} show under long term repeated use of this technique how often optimisation would be required.

>>>>

Thus, Figures \ref{fig:need-to-opt-1}, \ref{fig:need-to-opt-2} and \ref{fig:need-to-opt-3} show how often optimisation would be required
under long term repeated use of this technique.
